Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-26 paper/paper.tex
change is results table layout

\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Variants}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

@@

\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), and Remote Code Execution (RCE). Note
that the distribution of attacks is not uniform across types and
protocols as they are not uniform in practice. For example, as
per~\cite{emerging-threats-open}, RCE are the most prevalent type of
attacks today.\Mar{please, confirm} Columns ``Protocol'' and ``Ground
Truth'' indicate, respectively, that we analyzed attacks of different
protocols and analyzed different features of \tname.

>>>>

\setlength{\tabcolsep}{3pt}
\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    \multicolumn{1}{c}{\multirow{2}{*}{Name}} &
    \multicolumn{1}{c}{\multirow{2}{*}{\# Vars.}} &
    \#~Option Cand. &
    \#~Plausible Rules &    
    \multicolumn{1}{c}{Rank} \\

@@

This section describes the objects used in \tname{}'s evaluation.

\vspace{1ex}
\subsubsection{Attacks.}~Table~\ref{table:attacks} shows the selection
of attacks considered in our evaluation.  Column ``Name'' shows the
name of the attack, column ``Source'' shows the source where we
obtained data to reproduce the attack (see
Section~\ref{subsec:malicious-traffic}), column ``Type'' shows the
kind of attack, column ``Protocol'' shows the name of the protocol
explored in the attack, and column ``Ground Truth'' shows the rule
options to capture the attack. The rationale for the selection were
(1) to cover attacks with different characteristics, (2) to cover
attacks of various protocols, and (3) to explore different features of
\tname. As for (1), the selection includes attacks of the following
types: Denial-of-Service (DoS), Active Reconnaissance (AREC),
Privilege escalation (PESC), and Remote Code Execution (RCE). Note
that the distribution of attacks is not uniform across types and
protocols as these distributions are not uniform in practice. For
example, as per~\cite{emerging-threats-open}, RCE are the most
prevalent type of attacks today.\Mar{please, confirm} Columns
``Protocol'' and ``Ground Truth'' indicate, respectively, that we
analyzed attacks of different protocols and analyzed different
features of \tname.
